---
title: "kermit perception rank-based test"
author: "Yirui Zhang"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Yirui's first message in the document

Ted, collaborating.
- load the tidyverse
- read in the kermit data as "kermit"
- make some side-by-side histograms of the Score.pre for all respondents, separated by the Gender column

```{r}

library(tidyverse)

kermit <- read_csv("kermit.csv")

```

```{r}

kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender)

kermit_hist

```

Yirui:perform rank-based test using Mann-Whitney U and Wilcoxon-signed rank

Question: is there a significant difference in pre-talk ranks of kermit for male and female respondents?

```{r}
mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .) #use the previous data

#Null hypothesis: There is not a significant differenfce in ranks for male and female respondents

#Alternative: there is a significant difference

mwu_kermit

```

There was no significant difference in ranks for male and female respondents(W= 155.5, p = 0.4, alpha = 0.05) 

Next question (collaborators):

Is there a significant change in kermit ranking before and after his Bren talk?

```{r}

wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)

#H0: there is not a significant difference in ranks for pre and post talk scores

wsr_kermit

```

There is no significant difference in ranks for pre and post talk scores.